### 2015-02-22 fundamentals/acros.tex

\newacronym{RDD}{RD\&D}{Research Development and Design}

@@

\newacronym{CSNF}{CSNF}{Commercial Spent Nuclear Fuel}
\newacronym{DSNF}{DSNF}{DOE Spent Nuclear Fuel}
\newacronym{MTHM}{MTHM}{Metric Ton of Heavy Metal}
\newacronym{HTGR}{HTGR}{High Temperature Gas Reactor}

@@

\newacronym{MA}{MA}{Minor Actinide}

@@

\newacronym{STC}{STC}{Specific Temperature Change}
\newacronym{LDRD}{LDRD}{Laboratory Directed Research and Development}
\newacronym{LCOE}{LCOE}{Levelized Cost of Electricity}
\newacronym{ABM}{ABM}{Agent-Based Modeling}
\newacronym{COTS}{COTS}{Commercial, Off-The-Shelf}
\newacronym{API}{API}{Application Programming Interface}

@@

\newacronym{GUI}{GUI}{Graphical User Interface}
\newacronym{HPC}{HPC}{High-Performance Computing}
\newacronym{HTC}{HTC}{High-Throughput Computing}

@@

\newacronym{DAG}{DAG}{Directed Acyclic Graph}
\newacronym{MOX}{MOX}{Mixed Oxide}
\newacronym{UOX}{UOX}{Uranium Oxide}
\newacronym{QA}{QA}{Quality Assurance}

@@

\newacronym{VV}{V\&V}{Verification and Validation}
\newacronym{UQ}{UQ}{Uncertainty Quantification}

@@

\newacronym{CI}{CI}{Continuous Integration}
\newacronym{DRE}{DRE}{Dynamic Resource Exchange}

@@

\newacronym{MILP}{MILP}{Mixed-Integer Linear Program}
\newacronym{LP}{LP}{Linear Program}

>>>>

\newacronym{RDD}{RD\&D}{research development and design}

@@

\newacronym{CSNF}{CSNF}{commercial spent nuclear fuel}
\newacronym{DSNF}{DSNF}{DOE spent nuclear fuel}
\newacronym{MTHM}{MTHM}{metric ton of heavy metal}
\newacronym{HTGR}{HTGR}{high temperature gas reactor}

@@

\newacronym{MA}{MA}{minor actinide}

@@

\newacronym{STC}{STC}{specific temperature change}
\newacronym{LDRD}{LDRD}{laboratory directed research and development}
\newacronym{LCOE}{LCOE}{levelized cost of electricity}
\newacronym{ABM}{ABM}{agent-based modeling}
\newacronym{COTS}{COTS}{commercial, off-the-shelf}
\newacronym{API}{API}{application programming interface}

@@

\newacronym{GUI}{GUI}{graphical user interface}
\newacronym{HPC}{HPC}{high-performance computing}
\newacronym{HTC}{HTC}{high-throughput computing}

@@

\newacronym{DAG}{DAG}{directed acyclic graph}
\newacronym{MOX}{MOX}{mixed oxide}
\newacronym{UOX}{UOX}{uranium oxide}
\newacronym{QA}{QA}{quality assurance}

@@

\newacronym{VV}{V\&V}{verification and validation}
\newacronym{UQ}{UQ}{uncertainty quantification}

@@

\newacronym{CI}{CI}{continuous integration}
\newacronym{DRE}{DRE}{dynamic resource exchange}

@@

\newacronym{MILP}{MILP}{mixed-integer linear program}
\newacronym{LP}{LP}{linear program}
